Radial Velocity Upper Limits on Planets around Radio Exoplanet Candidates GJ~1151 and GJ~412A

### 2019-02-28 paper/ms.tex
more of the paper

>>>>

The results of this analysis conclusively rule out binary companions or planets on short orbits more massive than Neptune as the origin of the radio signals from GJ~1151 and GJ~412A. We nevertheless cannot rule out in either case planets less massive than a few Earth masses. Given that Vedantham et al. (submitted) find that even a planet with a mass around that of $\sim$Mercury could explain these signals, there is a very large region of parameter space for these planets that cannot be excluded and the planet hypothesis remains reasonable.
